Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-04 paper.tex
pu uncerintainty + adding discussion

@@

The fluctuation of the full relative uncertainty at low time are because of the
sensitivity to the fuel loading: all reactors at the beginning have synchronised
cycle, this phenomenon disappear with the gradual decommissioning of the initial
reactor, spread on 50 years.

@@

>>>>

Note: the fuel enrichment is determined by a fuel fabrication model\cite{leniau} which
express a fissile fraction required in the fuel to reach a target
burnup at the end of irradiation. In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to to a fuel enrichment uncertainty close to
$10\%$.

@@

The fluctuation of the full relative uncertainty at low time are because of the
sensitivity to the fuel loading: all reactors at the beginning have synchronised
cycle, this phenomenon disappears with the gradual decommissioning of the initial
reactor, spread on 50 years.

@@

\subsection{Fissile Inventory}
As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow on
year 40, with the deployment of the first reprocessing facility. It grows
during the first period of the \glspl{LWR} to \glspl{FBR}-A transition until
year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
When he steady state is reached (full \glspl{FBR} fleet), the plutonium
inventory starts to increase, as the breading ratio of the \glspl{FBR} is higher
than the deployment needs.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.35]{pu_full}
    \caption{Fissile (plutonium) inventory as a function of time. The black line
        represents the reference calculation and the blue zone
        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:pu_full}
\end{figure}

\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.35]{pu_uncer}
    \caption{Fissile (plutonium) inventory relative uncertainty, with
    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
    contribution of each parameter: cooling time (blue), fuel enrichment (red),
    cycle time (green), thermal power(brown), separation efficiency (light
    blue).}\label{fig:pu_uncer}
\end{figure}

Regarding the uncertainty, beside the low inventory artefact observable around
year 40, the relative uncertainty starts at about $5\%$, and grows until year
125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
it will reach an equilibrium between $5$ and $10\%$...
Between year 40 and 70, the main contributor to the fissile inventory
uncertainty is the cycle length, as for the uranium needs, lower cycle length
implies more fuel loads. Never the less, around year 65 (see Figure
\ref{fig:used_fuel}), the stock of used fuel available for reprocessing starts
to lack, and the availability of the used fuel starts to dictate the evolution
of fissile in storage. The uncertainty weight is then slowly transferred from
the cycle length to the fuel cooling time.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.17]{used_fuel}
    \caption{Used fuel inventory.}\label{fig:used_fuel}
\end{figure}
Between year 90 and 120, the \glspl{FBR} deployment speed increases, it has to
compensate the non replacement of the decommissioned \glspl{LWR} as well as
follow the power demand. During this period the needs in plutonium are higher
than its productions, explaining the observed decrease of the total amount, and
the increase associated relative uncertainty.

As the transition ends, the plutonium breed from the \glspl{FBR} starts to be
sufficient to sustain the new \glspl{FBR} deployment to follow the power demand.

It is also interesting to note that, the uncertainty contribution from the cycle
length are conversion toward the power contribution, such as the increase of
fuel loads effect tends to vanish and let its place to a discharge burnup
effect (the power uncertainty only affects the burnup of the fuel at discharge).

\section{Discussion}

Even if for the two output metric analysed there is no surprise such as the
identified uncertainty contributions, it is very interesting to be able to
measure them and rank them.

In this study, we can estimate than the cycle length uncertainty of $10\%$
varies from $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
on the enrichment implies a almost flat uncertainty of $2\%$, and the enrichment
tails uncertainty have an even lower contributions of $1\%$.

It is also very interesting to observe that while the plutonium inventory uncertainty
reach a pick at $30\%$, lead by the cooling time uncertainty contribution, the reactor
parameters seems to have a lower contribution, the cycle time contribution
picking at $10\%$ and stabilizing with the power contribution around $1\%$

Two main points can be deduced from this work. First of all, in a transitional
fuel cycle, the uncertainty contributions to an output metric can vary over time
depending of various factors: deployment schedule artifact or pressure point in
the material flows.
